Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-20 tex/paper1/paper1.tex
filled in the last part of the table

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & \multicolumn{3}{c}{lognormal $G(\nu)$} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$}      &
\colhead{$\delta$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{}          & 
\colhead{}      & 
\colhead{}      &
\colhead{} &
\colhead{(mHz)}      &
\colhead{(decades of frequency)}\\
}
\startdata
loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.28^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.34^{+0.07}_{-0.07}$ & $0.73^{+0.07}_{-0.06}$  & $0.32^{+0.01}_{-0.01}$  \\
                & 193\AA  & $0.21^{+0.02}_{-0.02}$  & $2.27^{+0.03}_{-0.03}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.24^{+0.09}_{-0.10}$ & $0.37^{+0.06}_{-0.04}$  & $0.40^{+0.01}_{-0.02}$  \\
                & & & & & & & \\

@@

\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt{2\pi\sigma^{2}}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$,
$N_{f}$ is the number of Fourier frequencies, and $\sigma_{j}$ is the
normal distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution, and are given
in Table \ref{tab:priors}.  Each MCMC chain that was run took 100,000
samples, with burn-in assumed to be at 50,000 samples.  The chain is
thinned by taking every fifth element in the chain, forming the final
sample from which the parameter estimates and their uncertainties are
calculated.
\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{parameter} &
\colhead{Model 1} &
\colhead{Model 2} \\
}
\startdata
$A$ & $4.5 \times 10^{-5} \rightarrow 22026$ &  $4.5 \times 10^{-5} \rightarrow 22026$\\
$n$  &  $-1\rightarrow 6$   & $-1\rightarrow 6$  \\
$C$ & $2.1 \times 10^{-9} \rightarrow 22026$  & $2.1 \times 10^{-9} \rightarrow 22026$  \\
$\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
$\beta$ & not applicable  & $0.5 - 10$\tablenote{???} (mHz)\\
$\delta$ & not applicable & $0.001\rightarrow 3$ (decades of frequency)\\
\enddata
\tablenote{???Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal
distribution to lie within the prior range.}
\end{deluxetable}
The \mFpa\ are assumed to
be normally distributed with a width given by $\sigma_{mean}$ as
calculated above.  A five step fitting process is used to fit Models 1
and 2 to the data, and is described below.

>>>>

\begin{deluxetable}{cccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.\label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & \multicolumn{3}{c}{lognormal $G(\nu)$} \\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$}      &
\colhead{$\delta$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{}          & 
\colhead{}      & 
\colhead{}      &
\colhead{} &
\colhead{(mHz)}      &
\colhead{(decades of frequency)}\\
}
\startdata
loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.28^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.34^{+0.07}_{-0.07}$ & $0.73^{+0.07}_{-0.06}$  & $0.32^{+0.01}_{-0.01}$  \\
                & 193\AA  & $0.06^{+0.02}_{-0.02}$  & $2.26^{+0.04}_{-0.04}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.30^{+0.18}_{-0.20}$ & $0.34^{+0.12}_{-0.08}$  & $0.41^{+0.03}_{-0.03}$  \\
                & & & & & & & \\

@@

\subsection{Model fitting and selection}
Equations \ref{eqn:pwrlaw} and \ref{eqn:pwrlawbump} are fit to the
geometric mean power spectra shown in Figures \ref{fig:fit171193}.  A
Bayesian/Markov chain Monte Carlo package (PyMC version 2.3,
\cite{Patil:Huard:Fonnesbeck:2010:JSSOBK:v35i04}) is used to construct
the Bayesian posterior and determine model parameter estimates and
their uncertainty.  If $P_{i,j}$ is the power at Fourier frequency
$\nu_{j}$ from Model $i$ then the likelihood $L$ is
\begin{equation}\label{eqn:likelihood}
L = \prod_{j=1}^{N_{f}}
\frac{1}{\sqrt{2\pi\sigma^{2}}}
\exp\left(
-\frac{(P_{i,j} - D_{j})^{2}}{2\sigma_{j}^{2}}
\right)
\end{equation}
where $D_{j}$ is the observed \mFps\ at frequency $\nu_{j}$,
$N_{f}$ is the number of Fourier frequencies, and $\sigma_{j}$ is the
normal distribution width at frequency $\nu_{j}$ .  Each of the priors for
the parameters in each model has a uniform distribution, and are given
in Table \ref{tab:priors}.  Each MCMC chain that was run took 100,000
samples, with burn-in assumed to be at 50,000 samples.  The chain is
thinned by taking every fifth element in the chain, forming the final
sample from which the parameter estimates and their uncertainties are
calculated.
\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize} 
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Priors for each of the parameters used in Model 1
  (Equation \ref{eqn:pwrlaw}) and
  Model 2 (Equation \ref{eqn:pwrlawbump}) \label{tab:priors}}
\tablehead{
\colhead{parameter} &
\colhead{Model 1} &
\colhead{Model 2} \\
}
\startdata
$A$ & $4.5 \times 10^{-5} \rightarrow 22026$ &  $4.5 \times 10^{-5} \rightarrow 22026$\\
$n$  &  $-1\rightarrow 6$   & $-1\rightarrow 6$  \\
$C$ & $2.1 \times 10^{-9} \rightarrow 22026$  & $2.1 \times 10^{-9} \rightarrow 22026$  \\
$\alpha$  & not applicable & $2.1 \times 10^{-9} \rightarrow 148$ \\
$\beta$ & not applicable  & $0.5 - 10$\tablenotemark{1} (mHz)\\
$\delta$ & not applicable & $0.001\rightarrow 3$ (decades of frequency)\\
\enddata
\tablenotetext{Model 2 for AIA 193\AA\ loop footpoint region required a uniform prior
for $\beta$ in the range $0.1 - 10$ mHz in order for its marginal
distribution to lie within the prior range.}
\end{deluxetable}
The \mFpa\ are assumed to
be normally distributed with a width given by $\sigma_{mean}$ as
calculated above.  A five step fitting process is used to fit Models 1
and 2 to the data, and is described below.
